### 2019-03-11 2-Chapters/4-Chapter/CrownCom_17.git/IoT_slotted.tex
Commence à intégrer changements d'Emilie, cf. #13

Where $(a)^{+} = \max(a,0)$, and $\mathcal{W}$ denotes the $\mathcal{W}$-Lambert function which is the reciprocal bijection of $x \mapsto x e^x$ on $\mathbb{R^+} = [0, +\infty)$ \cite{Corless96}.
Moreover, condition \eqref{eq:41:eqCstr} implies that the Lagrange multiplier $\lambda$ is the solution of the constraint
\begin{equation}\label{eq:41:constraintLambda}
 \sum_{i=1}^{K} D_i^*(\lambda) = D.
\end{equation}

>>>>

Where in the equation~\eqref{eq:41:Dilambda}, $(a)^{+} = \max(a,0)$, and $\mathcal{W}$ denotes the $\mathcal{W}$-Lambert function which is the reciprocal bijection of $x \mapsto x e^x$ on $\mathbb{R^+} = [0, +\infty)$ (it can be computed numerically in an efficient manner) \cite{Corless96}.
Moreover, condition \eqref{eq:41:eqCstr} implies that the Lagrange multiplier $\lambda$ is the solution of the constraint
\begin{equation}\label{eq:41:constraintLambda}
 \sum_{i=1}^{K} D_i^*(\lambda) = D.
\end{equation}
